Parallel global optimization algorithm with uniform convergence for solving a set of constrained global optimization problems\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2020-06-15 2020/OPTIMA/optima_paper.tex
OPTIMA: Fixes in formula and bib file

\begin{document}
%
\title{Parallel global optimization algorithm with uniform convergence
for solving a set of constrained global optimization problems\thanks{This study was supported
by the Russian Science Foundation, project No.\,16-11-10150.}}
%
\titlerunning{Parallel global optimization algorithm with uniform convergence}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Vladislav Sovrasov\and
Konstantin Barkalov
}
%
\authorrunning{V. Sovrasov et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia
\email{sovrasov.vladislav@itmm.unn.ru},
\email{konstantin.barkalov@itmm.unn.ru}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
In the present work, an extension of global optimization algorithm for solving a set of problems
simultaneously onto a case of problems with non-convex constraints is considered. The property
of uniform convergence inherent to the algorithm allows distributing the computation resources
in the optimal way since the errors of numerical solutions decrease with approximately equal
rates in all problems in the course of the execution of the algorithm. The algorithm assigns a
priority to each problem and performs the computations of the objective functions in several
problems in parallel at every iteration. Upon stop of the method at arbitrary time moment,
solutions of similar quality would be obtained in all problems of the series being solved. A series
of several problems arises if the global optimization problem has a discrete parameter or, for
example, in solving a multicriteria optimization problem using criteria convolution. The
considered algorithm employs Peano-type space-filling curves for the reduction of the
multidimensional optimization problems to the one-dimensional ones.  The efficiency of the
implemented algorithm was tested using the sets of artificially generated global optimization
problems as well as in solving a series of problems obtained as a result of scalarization of a
multicriteria optimization  problem. Also, the numerical experiments confirmed the uniform
convergence of the proposed method.

@@

  If \(\nu(w_{j-1})=\nu(w_{j})=\alpha\) then the first branch of the rule (\ref{step3_1}) is applied and
  \begin{dmath}
    R_\psi(j)=\Delta_j + \frac{(w_j-w_{j-1})^2}{r_\alpha^2\mu_{\psi,\alpha}^2\Delta_j}
      - \frac{2(w_j+w_{j-1}-2w^*_\alpha)}{r_\alpha\mu_{\psi,\alpha}} \geqslant
      \Delta_j - \frac{2(w_j+w_{j-1}-2w^*_\alpha)}{r_\alpha\mu_{\psi,\alpha}} =
      \Delta_j - \frac{2\Delta_j(w_{j-1}-w_j)}{r_\alpha\mu_{\psi,\alpha}\Delta_j} \geqslant
      \Delta_j - \frac{\Delta_j}{r_\alpha} = \Delta_j\left(1-\frac{1}{r_\alpha}\right).
    \label{eq:th4}
  \end{dmath}

>>>>

\begin{document}
%
\title{Parallel global optimization algorithm with uniform convergence
for solving a set of constrained global optimization problems\thanks{This study was supported
by the Russian Science Foundation, project No.\,16-11-10150.}}
%
\titlerunning{Parallel global optimization algorithm with uniform convergence}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Vladislav Sovrasov\and
Konstantin Barkalov
}
%
\authorrunning{V. Sovrasov et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia
\email{sovrasov.vladislav@itmm.unn.ru},
\email{konstantin.barkalov@itmm.unn.ru}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
In the present work, an extension of global optimization algorithm for solving a set of problems
simultaneously onto a case of problems with non-convex constraints is considered. The property
of uniform convergence inherent to the algorithm allows distributing the computation resources
in the optimal way since the errors of numerical solutions decrease with approximately equal
rates in all problems in the course of the execution of the algorithm. The algorithm assigns a
priority to each problem and performs the computations of the objective functions in several
problems in parallel at every iteration. Upon stop of the method at arbitrary time moment,
solutions of similar quality would be obtained in all problems of the series being solved. A series
of several problems arises if the global optimization problem has a discrete parameter or, for
example, in solving a multicriteria optimization problem by applying scalarization techniques. The
considered algorithm employs Peano-type space-filling curves for the reduction of the
multidimensional optimization problems to the one-dimensional ones.  The efficiency of the
implemented algorithm was tested using the sets of artificially generated global optimization
problems as well as in solving a series of problems obtained as a result of scalarization of a
multicriteria optimization  problem. Also, the numerical experiments confirmed the uniform
convergence of the proposed method.

@@

  If \(\nu(w_{j-1})=\nu(w_{j})=\alpha\) then the first branch of the rule (\ref{step3_1}) is applied and
  \begin{equation}
    \begin{array}{l}
      R_\psi(j)=\Delta_j + \frac{(w_j-w_{j-1})^2}{r_\alpha^2\mu_{\psi,\alpha}^2\Delta_j}
        - \frac{2(w_j+w_{j-1}-2w^*_\alpha)}{r_\alpha\mu_{\psi,\alpha}} \geqslant \\
        \geqslant\Delta_j - \frac{2(w_j+w_{j-1}-2w^*_\alpha)}{r_\alpha\mu_{\psi,\alpha}} =
        \Delta_j - \frac{2\Delta_j(w_{j-1}-w_j)}{r_\alpha\mu_{\psi,\alpha}\Delta_j} \geqslant\\
        \geqslant \Delta_j - \frac{2\Delta_j}{r_\alpha} = \Delta_j\left(1-\frac{2}{r_\alpha}\right).
      \end{array}
    \label{eq:th4}
  \end{equation}
